\documentclass[alpha-refs]{wiley-article}

\usepackage[binary-units]{siunitx}
\usepackage{bm,bbm}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{float}
\usepackage{rotating}
\graphicspath{{./Figures/}}
\usepackage[linesnumbered,lined,boxed]{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
\makeatother
\usepackage{undertilde}
\usepackage{todonotes}
\usepackage{comment}   

\DeclareSIUnit{\minusalphapercent}{(1-\alpha)\%}
\DeclareSIUnit{\alphapercent}{\alpha\%}

\newcommand{\Mycite}[1]{%
 (\citeauthor{#1},~\citeyear{#1})}

\papertype{Original Article}

\title{A Test for White Noise in the Entropy-Complexity Plane}

\abbrevs{RNG, random number generator; PRNG, pseudorandom number generator; TWNRS, true white noise random sequence.}

\author[1]{Eduarda T.\ C.\ Chagas}
\author[2,3]{Marcelo Queiroz}
\author[4]{Osvaldo A.\ Rosso}
\author[1]{Heitor S.\ Ramos}
\author[2]{Cristopher G.\ S. Freitas}
\author[2]{Leonardo V.\ Pereira}
\author[4]{Alejandro C.\ Frery}

\contrib[]{All authors contributed equally.}

% Include full affiliation details for all authors
\affil[1]{Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
\affil[2]{Laborat\'orio de Computa\c c\~ao Cient\'ifica e An\'alise Num\'erica, Universidade Federal de Alagoas, Brazil}
\affil[3]{Coordena\c c\~ao de Inform\'atica, Instituto Federal de Alagoas, Brazil}
\affil[4]{Instituto de F\'isica, Universidade Federal de Alagoas, Brazil}
\affil[5]{School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}

\corraddress{Eduarda T.\ C.\ Chagas, Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
\corremail{eduarda.chagas@dcc.ufmg.br}


\fundinginfo{CNPq, Fapeal}

% Include the name of the author that should appear in the running header
\runningauthor{Eduarda T.\ C.\ Chagas et al.}

\begin{document}	

% \begin{frontmatter}
\maketitle

\begin{abstract}
The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series, 
by computing Information Theory descriptors of the histogram of ordinal patterns.
Such descriptors lie in a 2D manifold: the Entropy-Complexity plane.
This article proposes the first approach that uses the entropy-complexity plane to test the white noise hypothesis.
Our test is based on true white noise sequences obtained from physical devices.
The proposed methodology provides consistent results, 
managing to assess sequences of true random samples as random (adequate size), 
rejecting correlated sequences (sound power), and
capturing the randomness of generators previously analyzed in the literature.
\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Time Series, Information Theory}
\end{abstract}

\input{Chapters/Introduction}
\input{Chapters/Background}
\input{Chapters/Methodology}
\input{Chapters/Results}
\input{Chapters/Conclusions}
\input{Chapters/Source}
\input{Chapters/acknowledgements}

\printendnotes

\bibliography{References}

\end{document}