\documentclass[alpha-refs]{wiley-article}

\usepackage[binary-units]{siunitx}
\usepackage{bm,bbm}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{float}
\usepackage{rotating}
\graphicspath{{./Figures/}}
\usepackage[linesnumbered,lined,boxed]{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
\makeatother
\usepackage{undertilde}

\usepackage{todonotes}
\usepackage{comment}   

\DeclareSIUnit{\minusalphapercent}{(1-\alpha)\%}
\DeclareSIUnit{\alphapercent}{\alpha\%}

\newcommand{\Mycite}[1]{%
 (\citeauthor{#1},~\citeyear{#1})}

\papertype{Original Article}

\title{Time Series Analysis with Bandt \& Pompe Symbolization and a Test for White Noise in the Entropy-Complexity Plane}

\abbrevs{RNG, random number generator; PRNG, pseudorandom number generator; TWNRS, true white noise random sequence.}

\author[1]{Eduarda T.\ C.\ Chagas}
\author[2,3]{Marcelo Queiroz-Oliveira}
\author[4]{Osvaldo A.\ Rosso}
\author[1]{Heitor S.\ Ramos}
\author[2]{\mbox{Cristopher G.\ S. Freitas}}
\author[5]{Alejandro C.\ Frery}

\contrib[]{All authors contributed equally.}

% Include full affiliation details for all authors
\affil[1]{Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
\affil[2]{Laborat\'orio de Computa\c c\~ao Cient\'ifica e An\'alise Num\'erica, Universidade Federal de Alagoas, Brazil}
\affil[3]{Coordena\c c\~ao de Inform\'atica, Instituto Federal de Alagoas, Brazil}
\affil[4]{Instituto de F\'isica, Universidade Federal de Alagoas, Brazil}
\affil[5]{School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}

\corraddress{Eduarda T.\ C.\ Chagas, Departamento de Ci\^encia da Computa\c c\~ao, Universidade Federal de Minas, Brazil}
\corremail{eduarda.chagas@dcc.ufmg.br}


\fundinginfo{CNPq, Fapeal}

% Include the name of the author that should appear in the running header
\runningauthor{Eduarda T.\ C.\ Chagas et al.}

\begin{document}	

% \begin{frontmatter}
\maketitle

\begin{abstract}
This article serves two purposes.
Firstly, it surveys the \citeauthor{PermutationEntropyBandtPompe} methodology for the statistical community, stressing topics that are open for research.
Secondly, it contributes towards a better understanding of the statistical properties of that approach for time series analysis.
%
The \citeauthor{PermutationEntropyBandtPompe} methodology 
%has been used successfully in the analysis of time series. 
%It 
consists of computing
Information Theory descriptors of the histogram of ordinal patterns. 
Such descriptors lie in a 2D manifold: the Entropy-Complexity plane. 
This article provides the first proposal
of a test in the Entropy-Complexity plane for the
white noise hypothesis.
Our test is based on true white noise sequences obtained from physical devices.
The proposed methodology provides consistent results, 
managing to assess sequences of true random samples as random (adequate test size), 
rejecting correlated sequences (sound test power), and
capturing the randomness of generators previously analyzed in the literature.
\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Time Series, Information Theory}
\end{abstract}

\input{Chapters/Introduction}
\input{Chapters/Background}
\input{Chapters/Methodology}
\input{Chapters/Results}
\input{Chapters/Conclusions}
\input{Chapters/Source}
\input{Chapters/acknowledgements}

\printendnotes

\bibliography{References}

\end{document}